Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Pad out discussion/future work and conclusion

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure}

@@

\begin{table}[H]
  \begin{tabular*}{\linewidth}{lr}
    \toprule
    Protocol & Identified as Tor\\
    \midrule
    HTTPS & 0.0000\% \\
    HTTP over Tor & 0.9903\% \\
    HTTPS over Tor & 0.9826\% \\
    \bottomrule
  \end{tabular*}
  \caption{Results}
  \label{table:heuristic-results}
\end{table}

@@

@@

>>>>

\begin{figure}[h]
  \centering\includegraphics[width=\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure}

\begin{figure}[h]
  \centering\includegraphics[width=\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure}

\begin{figure}[h]
  \centering\includegraphics[width=\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure}

@@

\begin{table}[h]
  \begin{tabular*}{\linewidth}{lr}
    \toprule
    Protocol & Identified as Tor\\
    \midrule
    HTTPS & 0.0000\% \\
    HTTP over Tor & 0.9903\% \\
    HTTPS over Tor & 0.9826\% \\
    \bottomrule
  \end{tabular*}
  \caption{Results}
  \label{table:heuristic-results}
\end{table}

@@

\section{Discussion}

The encryption layers that wrap Tor level communications, do not
appear to obfuscate the size of communications sent between Tor nodes. This is
most apparent in the composition of packet sizes that make up an individual
session, with Tor sessions showing a large percentage of packets just large
enough to fit the 512 byte cells that make up the Tor protocol.

\section{Future Research}

Training a classifier against real world traffic will account for the different
and varied nature of packet switching hardware, with different maximum
transmission units, performance capabilities and geographic location.

The heuristic based classifier used in this paper used a single attribute: the
size of individual packets in a stream, to classify with great accuracy. But
other attributes may be considered, the most typical of these being inter
packet arrival time - though this is likely to be more affected by natural
variability.

The encrypted traffic generated in the first phase of the experiment, only
covered a single application and version. It may be possible that other
applications use the same protocol with encryption and have characteristics
similar to that produced by Tor. This would lead to any proposed classifier
generating false positives. Further research should also consider the nature
and characteristics of a wider set of encrypted communications.

@@

This research demonstrates that Tor does have characteristics that make it
distinguishable from regular encrypted traffic. The encryption used by Tor does
not appear to blur the size of communication cells sufficiently to prevent
automated identification of Tor traffic, even with only a few observed packets.
While the scope of this research is limited, it suggests that it may be
possible to build simple software to automatically identify Tor users and block
them from the network.
